Optimizing Congestion Control Through Fair Queuing Detection

### 2020-10-20 paper/paper.tex
Add reference

\def\anonymize{yes}
\def\tempYes{yes}
\def\tempNo{no}

@@

%JF: Evtl.statt subsubsection Absätze mit Titel fett verwenden um doch einigen Platz zu sparen?
\subsubsection{\gls{cc} using Active Measurements}
Several approaches have been recently proposed which aim to incorporate active measurements into \glspl{cca}. \cite{dong_pcc_2015,dong_pcc_2018} introduced the \gls{cca} \textit{PCC}, which uses active measurements to find the sending rate which optimizes a given reward function. \cite{cardwell_bbr:_2016} introduce the \textit{BBR} \gls{cca}, which uses active measurement to create a model of the network connection. This model is then used to determine the optimal sending rate. \cite{bachl_rax_2019} use Reinforcement Learning to learn \gls{cc} policies. This is done by performing active measurements by varying the congestion window to evaluate which value gives the highest throughput and lowest packet loss.

%JF: Evtl.statt subsubsection Absätze mit Titel fett verwenden um doch einigen Platz zu sparen?
\subsubsection{Flow startup techniques} Besides the classical TCP slow start algorithm \cite{stevens_tcp_1997} some other proposals were made such as Quick Start \cite{jain_quick-start_2019}, which aims to speed up flow start by routers informing the end point, which rate they deem appropriate. \cite{jarvinen_congestion_2019} investigate the impact of \gls{aqm} and \gls{cc} during flow startup. They inspect a variety of different \gls{aqm} algorithms and also investigate \gls{fq}. \cite{kuhlewind_chirping_2010} propose ``chirping'' for flow startup to estimate the available bandwidth. This works by sending packets with different gaps between them to verify what the actual link speed is. \cite{mittal_recursively_2014} propose speeding up flow startup by using packets of different priority. The link is flooded with low-priority packets and in case the link is not fully utilized during startup, these low-priority packets are going to be transmitted, allowing the starting flow to achieve high throughput. If the link is already saturated, the low-priority packets are going to be discarded and no other flow suffers.

@@

Besides the examples we provided, we also conducted a more systematic comparison of the throughput and delay that our algorithm achieves: We use the same scenario as above and again vary bandwidth from 5 to 50\,Mbps, delay from 10 to 100\,ms and the buffer size from 1 to 100 packets. For each parameter, we take 5 values, evenly spaced, totaling 125 distinct scenarios. We use \gls{fq} at the bottleneck link. We run each scenario both using Cubic as well as our algorithm for 30 seconds each. We average the achieved throughputs and average delays from all experiments for both Cubic as well as our algorithm. For Cubic, the mean throughput is 21\,Mbit/s and the mean \gls{rtt} is 96\,ms while for our algorithm it is 26\,Mbit/s and 64\,ms. This shows that our algorithm can correctly determine that there is \gls{fq} and switch to the delay-based \gls{cc} and that our algorithm achieves significantly lower delay (Cubic's delay is 50\% higher) and higher throughput. This is a bit surprising, our algorithm also achieves higher throughput, which is astonishing considering that loss-based \glspl{cca} such as Cubic should be more aggressive in filling the link. When analyzing the results we identified that Cubic performs very poorly in scenarios with small buffers because the multiplicative decrease of Cubic is 0.7, meaning that the bandwidth is reduced by 30\% after every packet loss while our algorithm only reduces it by only 5\%. Thus Cubic reduces bandwidth too much after packet loss which results in underutilization of the link.

>>>>

\def\anonymize{no}
\def\tempYes{yes}
\def\tempNo{no}

@@

\subsubsection{\gls{cc} using Active Measurements}
Several approaches have been recently proposed which aim to incorporate active measurements into \glspl{cca}. \cite{dong_pcc_2015,dong_pcc_2018} introduced the \gls{cca} \textit{PCC}, which uses active measurements to find the sending rate which optimizes a given reward function. \cite{cardwell_bbr:_2016} introduce the \textit{BBR} \gls{cca}, which uses active measurement to create a model of the network connection. This model is then used to determine the optimal sending rate. \cite{bachl_rax_2019} use Reinforcement Learning to learn \gls{cc} policies. This is done by performing active measurements by varying the congestion window to evaluate which value gives the highest throughput and lowest packet loss. Another approach proposed by \cite{goyal_elasticity_2018} aims to differentiate bulk transfer flows, which they deem ``elastic'' because they try to grab as much bandwidth as available, from other flows that send at a constant rate, which they call ``unelastic''. They use this elasticity detection to determine if delay-based \gls{cc} can be used or not. If cross traffic is deemed elastic then they use classic loss-based \gls{cc} and otherwise delay-based \gls{cc}.

\subsubsection{Flow startup techniques} Besides the classical TCP slow start algorithm \cite{stevens_tcp_1997} some other proposals were made such as Quick Start \cite{jain_quick-start_2019}, which aims to speed up flow start by routers informing the end point, which rate they deem appropriate. \cite{jarvinen_congestion_2019} investigate the impact of \gls{aqm} and \gls{cc} during flow startup. They inspect a variety of different \gls{aqm} algorithms and also investigate \gls{fq}. \cite{kuhlewind_chirping_2010} propose ``chirping'' for flow startup to estimate the available bandwidth. This works by sending packets with different gaps between them to verify what the actual link speed is. \cite{mittal_recursively_2014} propose speeding up flow startup by using packets of different priority. The link is flooded with low-priority packets and in case the link is not fully utilized during startup, these low-priority packets are going to be transmitted, allowing the starting flow to achieve high throughput. If the link is already saturated, the low-priority packets are going to be discarded and no other flow suffers.

@@

Besides the examples we provided, we also conducted a more systematic comparison of the throughput and delay that our algorithm achieves: We use the same scenario as above and again vary bandwidth from 5 to 50\,Mbps, delay from 10 to 100\,ms and the buffer size from 1 to 100 packets. For each parameter, we take 5 values, evenly spaced, totaling 125 distinct scenarios. We use \gls{fq} at the bottleneck link. We run each scenario both using Cubic as well as our algorithm for 30 seconds each. We average the achieved throughputs and average delays from all experiments for both Cubic as well as our algorithm. For Cubic, the mean throughput is 21\,Mbit/s and the mean \gls{rtt} is 96\,ms while for our algorithm it is 26\,Mbit/s and 64\,ms. This shows that our algorithm can correctly determine that there is \gls{fq} and switch to the delay-based \gls{cc} and that our algorithm achieves significantly lower delay (loss-based Cubic's delay is 50\% higher) and -- surprisingly -- higher throughput. This is astonishing considering that loss-based \glspl{cca} such as Cubic should be more aggressive in filling the link. When analyzing the results we identified that Cubic performs very poorly in scenarios with small buffers because the multiplicative decrease of Cubic is 0.7, meaning that the bandwidth is reduced by 30\% after every packet loss while our algorithm only reduces it by only 5\%. Thus Cubic reduces bandwidth too much after packet loss which results in underutilization of the link.
